Information Disclosure in Dynamic Innovation Contests

### 2025-06-04 paper/Paper.tex
update

This paper focuses on the two players innovation contest with a continuous time  where the players’ relative position is public information throughout the game.
This is closely related to tug-or-war contest, which, to our knowledge, was first formally given by \citet{Harris1987Race} as a one-dimensional simplification of the multi-stage R\&D race. 
The output processes are model by Brownian motions drifted with effort inputs, which is followed by \cite{budd1993model} who model the state of a dynamic competition of two innovative duopoly firms by a Brownian motion drifted by the effort gap, and solve the equilibrium approximately. 
Furthermore, \citet{Moscarini2011Contest} model the tug-of-war state as the gap of the two outputs directly, and draw an analytical equilibrium of the pure strategies.

>>>>

This study is closely related to three strands of literature:

\subsubsection{Contest Design.}

%
A rich literature in contest design \citep{Ales2017Contest} has examined how to structure competitive environments to elicit optimal performance, with a primary focus on static settings. 
This line of research is motivated by a wide range of real-world applications, including 
CEO contest \citep{tsoulouhas2006ceo}, 
beauty contest \citep{morris2002social}, 
election campaigns \citep{denter2020campaign}, 
advertising contest \citep{dockner2018Advertising}, 
litigation \citep{baik2007litigation, park2022litigation} and 
innovation contest \citep{chen2021DataSharing}. 
This paper focuses on online crowdsourcing contests, which feature public real-time feedback, fixed deadlines, and repeated submissions, all governed by platform-specified rules and evaluation metrics. 
These features create a dynamic setting where participants adapt strategically, making such contests amenable to game-theoretic modeling.

%

%
Classic studies on static contest design have examined how different design levers affect participant behavior and outcomes. 
These include the allocation of awards \citep{ales2017optimal_award}, the timing and structure of feedback \citep{mihm2019feedback, Bimpikis2019Contest, jiang2022role}, the information disclosed to players \citep{aoyagi2010information}, the contest’s duration \citep{korpeoglu2021duration}, and participation rules \citep{Ales2021Innovation, stouras2022role}.

While these studies offer valuable insights into optimal incentive design, they largely abstract away from the intertemporal dynamics of strategic interaction. In contrast, our work focuses on dynamic contests in which participants adjust their efforts over time in response to evolving feedback and competition, requiring a different modeling and estimation approach.

% dynamic contest
This paper focuses on the two players innovation contest with a continuous time  where the players’ relative position is public information throughout the game.
This is closely related to tug-or-war contest, which, to our knowledge, was first formally given by \citet{Harris1987Race} as a one-dimensional simplification of the multi-stage R\&D race. 
The output processes are model by Brownian motions drifted with effort inputs, which is followed by \cite{budd1993model} who model the state of a dynamic competition of two innovative duopoly firms by a Brownian motion drifted by the effort gap, and solve the equilibrium approximately. 
Furthermore, \citet{Moscarini2011Contest} model the tug-of-war state as the gap of the two outputs directly, and draw an analytical equilibrium of the pure strategies.
